Machine Learning and Constraint Programming for Relational-To-Ontology Schema Mapping

### 2017-09-02 stp/paper_aaai/main.tex
Small fix

\end{tikzpicture}
\caption{Example of ontology
(`\tikz{ \node[class] () at (0,0)  {};}' are Classes, `\tikz{ \path[hasaC,->] 
(0,1) -- (3ex,1);}' means ``has an object property'', 
`\tikz{ \path[hasaA,decoration={post length=0}] (0,0) edge[decorate] (3ex,0);}' 
means ``has a data property'' and 
`\tikz{ \path[isa,->] (0,1) -- (3ex,1);}' means ``is a'' ). Example by
\citeasnoun{Taheriyan2013}.
}
\label{FIG:onto}
\end{figure}

@@

\end{scope}
\end{tikzpicture}
\caption{Examples of two semantic models (`\tikz{ \node[class] () at (0,0)  
{};}' are class nodes, and `\tikz{ \node[data] () at (0,0)  {};}' are data 
nodes).}
\label{FIG:sem}
\end{figure}

@@

\end{tikzpicture}
\caption{Example of alignment graph (`\tikz{ \node[class] () at (0,0)  
{};}' `\tikz{ \node[class,orange,fill=orange!30!white,text=black] () at 
(0,0)  
{};}' are class nodes, and `\tikz{ \node[data] () at (0,0)  {};}' are data 
nodes). We omit weights for clarity.}
\label{FIG:ali}
\end{figure}

@@

We choose a search strategy that will first try to match attributes using the cheapest edges in $\mathcal{M}_\mathcal{O}^{s^\star}$. Then, it will try to use the cheapest unfixed edge $e\in\mathcal{E_O}$ that completes a pattern $p$ such that $w_\mathcal{P}(p) > w_\mathcal{O}(e)$ or simply the cheapest edge if none complete a pattern.

>>>>

\end{tikzpicture}
\caption{Example of ontology
(`\tikz{ \node[class, inner sep = 2] () at (0,0)  {};}' are Classes, `\tikz{ \path[hasaC,->] 
(0,1) -- (3ex,1);}' means ``has an object property'', 
`\tikz{ \path[hasaA,decoration={post length=0}] (0,0) edge[decorate] (3ex,0);}' 
means ``has a data property'' and 
`\tikz{ \path[isa,->] (0,1) -- (3ex,1);}' means ``is a'' ). Example by
\citeasnoun{Taheriyan2013}.
}
\label{FIG:onto}
\end{figure}

@@

\end{scope}
\end{tikzpicture}
\caption{Examples of two semantic models (`\tikz{ \node[class, inner sep = 2] () at (0,0)  
{};}' are class nodes, and `\tikz{ \node[data] () at (0,0)  {};}' are data 
nodes).}
\label{FIG:sem}
\end{figure}

@@

\end{tikzpicture}
\caption{Example of alignment graph (`\tikz{ \node[class, inner sep = 2] () at (0,0)  
{};}' `\tikz{ \node[class,orange,fill=orange!30!white,text=black, inner sep = 2] () at 
(0,0)  
{};}' are class nodes, and `\tikz{ \node[data] () at (0,0)  {};}' are data 
nodes). We omit weights for clarity.}
\label{FIG:ali}
\end{figure}

@@

We choose a search strategy that will first try to match attributes using the cheapest edges in $\mathcal{M}_\mathcal{O}^{s^\star}$. Then, it will try to use the cheapest unfixed edge $e\in\mathcal{E_O}$ that fills a pattern $p$ (i.e. $\forall e_p\in p, e_p \neq e, c_{e_p}$) such that $w_\mathcal{P}(p) > w_\mathcal{O}(e)$ or simply the cheapest edge if none fill a pattern.
